

\makeheading{Emil Rehnberg}

%
% Contact Information
%
\section{Contact Information}
\newlength{\rcollength}\setlength{\rcollength}{2.15in}%1.85in
\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
111-0056	& \textit{Mobile:} 080-8034-6270 \\
Tokyo-to, Taito-ku, Kojima 1-1-8 Konsheria 603	& \textit{E-mail:} \email{emil.rehnberg@gmail.com}\\
Japan
\end{tabular}

%
% Citizinship
%
\section{Citizenship}
Swedish and Finnish

%
% Education
%
\section{Education}
\href{http://www.su.se/}{\textbf{Stockholm University}}, Stockholm, SWEDEN
\begin{outerlist}
\item[]	Magister Scientae, \href{http://math.su.se/}{Mathematical Statistics}, May 2009
        \begin{innerlist}
        \item Thesis Topic: \emph{Evaluation of a multipoint method for imputing genotypes using HapMap III}
        \item Supervisors:
              \href{juni.palmgren@ki.se}{Juni Palmgren}
              \href{keith.humphreys@ki.se}{Keith Humphreys}
              \href{monica.leu@ki.se}{Monica Leu}
        \item Area of Study: Biostatistics (genetics)
        \end{innerlist}
\end{outerlist}

%
% Professional experience
%
\section{Professional / Academic Experience}
%
\href{http://www.ncc.go.jp/en/nccri/divisions/14carc/14carc.html}{\textbf{Division of Epigenomics}}
\href{http://www.ncc.go.jp/}{\textbf{National Cancer Centre}}, Tsukiji, Tokyo, Japan
\begin{outerlist}

\item[] \textit{Biostatistician}%
	\hfill \textbf{February 2012 to Present}
\begin{innerlist}
\item Statistical consultant / informatician for researchers (Geneticists, Medical doctors).
\item Researcher
\item Bioinformatician
\end{innerlist}
\end{outerlist}

\halfblankline


\href{http://ki.se/ki/jsp/polopoly.jsp?d=9600}{\textbf{Department of Medical Epidemiology and Biostatistics}}
\href{http://www.ki.se/}{\textbf{Karolinska Institutet}}, Solna, Stockholm, Sweden
\begin{outerlist}

\item[] \textit{Biostatistician}%
        \hfill \textbf{December 2009 to January 2012 (currently on leave)}
\begin{innerlist}
\item Statistical consultant for multiple research projects.
\item Statistical consultant for PhD-students. Project planning, analysis, data management, methods.
\item Teaching assistant in biostatistic courses.
\end{innerlist}

\item[] \textit{Research Assistant}%
        \hfill \textbf{June 2009 to December 2009}
\\ Collaborators: Juni Palmgren, Keith Humphreys and Monica Leu
\begin{innerlist}
  \item Imputation of genotypes for NordicDB
  \begin{innerlist}
    \item Responsible for imputation of genotype data, genome-wide for NordicDB, which is a nordic database for genome-wide genetic information from controls (genotypes and allele frequences).
    \item Paper: NordicDB: a Nordic pool and portal for genome-wide control data, European Journal of Human Genetics , (28 July 2010)
  \end{innerlist}
\end{innerlist}

\end{outerlist}

\halfblankline

\href{http://www.matteakuten.se}{\textbf{Matteakuten}}, Stockholm, Sweden
\begin{outerlist}

\item[] \textit{Math teacher}%
        \hfill \textbf{September 2007 to January 2008}
\begin{innerlist}
\item Employed as a math teacher at upper secondary school level. (As extra work during university studies) 
\end{innerlist}

\end{outerlist}

%
% Submitted Journal Publications
%
\section{Submitted\\Journal\\Publications} \begin{bibsection}
\item Kim JG er al.
	Comprehensive DNA methylation and extensive mutation analyses reveal an association between the CpG island methylator phenotype and oncogenic mutations in gastric cancers.
	\emph{Cancer Letters} 2012 Nov 27
\item Scott RA et al.
	Large-scale association analyses identify new loci influencing glycemic traits and provide insight into the underlying biological pathways.
	\emph{Nat Genet.} 2012 Aug 12
    \item DIAGRAM consortium
	Large-scale association analysis provides insights into the genetic architecture and pathophysiology of type 2 diabetes.
	\emph{Nat Genet.} 2012 Aug 12
    \item Manning AK et al.
	A genome-wide approach accounting for body mass index identifies genetic variants influencing fasting glycemic traits and insulin resistance.
	\emph{Nat Genet.} 2012 May 13
    \item Stolk L et al.
	Meta-analyses identify 13 loci associated with age at menopause and highlight DNA repair and immune pathways.
	\emph{Nat Genet.} 2012 Jan 22
    \item Smedby KE et. al.
	GWAS of Follicular Lymphoma Reveals Allelic Heterogeneity at 6p21.32 and Suggests Shared Genetic Susceptibility with Diffuse Large B-cell Lymphoma.
	\emph{PLoS Genetics} 2011 April. 
    \item Monica Leu, Keith Humphreys, Ida Surakka, Emil Rehnberg, .. Juni Palmgren, Samuli Ripatti. 
	NordicDB: A Nordic pool and portal for genome-wide control data. 
	\emph{European Journal of Human Genetics}. 2010 December.
    \item Emil Rehnberg. 
	Evaluation of a multipoint method for imputing genotypes using HapMap III.
	Master’s thesis, Karolinska Institutet, Department of Medical Epidemiology and Biostatistics, 2009.
\end{bibsection}

%
% Papers in preparation 
%
%\section{Papers in Preparation} \begin{bibsection}
%    \item Kathy Lunetta et. al.
%	Meta-analysis of age at menopause identifies multiple novel loci highlighting DNA repair and aging pathways.
%    \item Linda Halldner, Emil Rehnberg, Niklas L\aa ngstr\"{o}m, Cecilia Lundholm, Marcus Boman, Paul Lichtenstein.
%        Birth month as a risk factor for ADHD in Sweden.
%\end{bibsection}

%
% Teaching experience
%
\section{Teaching Experience}
\href{http://ki.se/ki/jsp/polopoly.jsp?d=9600}{\textbf{Department of Medical Epidemiology and Biostatistics}}, Solna, Stockholm, Sweden
\begin{outerlist}
\item[] \textit{Teaching Assistant}
    \hfill \textbf{December 2009 to May 2011}
    \begin{innerlist}

        \item Master's Programme in Biomedicine, Biostatistics course
        \begin{innerlist}
	    \item Teaching assistant for pen \& paper exercises and computer labs. Descriptive, univariate, multivariate analysis, logistic regression. 
        \end{innerlist}

        \halfblankline

        \item Bachelor's Programme in Biomedicine, Biostatistics course
        \begin{innerlist}
	    \item R and R-commander introduction lecture.
	    \item Teaching assistant for pen \& paper exercises and computer labs.
        \end{innerlist}

        \halfblankline

	\item Biostatistics for Molecular Oncology course.
        \begin{innerlist}
            \item Statistical consulting for group discussions. Descriptive stats and survival analysis in R.
	    \item Teaching assistant for pen \& paper exercises and computer labs.
        \end{innerlist}

    \end{innerlist}
\end{outerlist}

\section{Professional activities}
\textit{The Swedish Society for Medical Statistics - 2011}
\begin{innerlist}
    \item{Board member}
    \item{Website manager}
\end{innerlist}

%
% Expertise
%
\section{Expertise}
\textit{Mathematics:}
\begin{innerlist}
    \item Applied mathematics, linear algebra, multivariate analysis
\end{innerlist}

\halfblankline

\textit{Statistics/Biostatistics:}
\begin{innerlist}
    \item Epidemiology, descriptive statistics, multivariate analysis, analysis of cathegorical data, stochastic processes, probability theory, survival analysis, prediction, principal component analysis, hierarchical clustering, supervised classification, motif analysis.
\end{innerlist}

%
% Software skills
%
\section{Software Skills}
\textit{Programming:}
\begin{innerlist}
    \item Advanced knowledge: R, SAS, Bash shell scripting.
    \item Basic knownledge: Ruby, Rails, parallel computing.
    \item Exposure to: SQL, HTML, Haml, Pascal, Scheme, Python, C\#, Fortran, C.
\end{innerlist}

\halfblankline

\textit{Applications:}
\begin{innerlist}
\item PLINK, multiple UNIX-based genetic software.
\end{innerlist}

\halfblankline

\textit{Productivity Applications:}
\begin{innerlist}
\item \TeX{}, Vim, git, UNIX tools such as: awk, sed, tmux, screen, etc.
\end{innerlist}

\halfblankline

\textit{Operating systems:}
\begin{innerlist}
    \item Ubuntu, Apple OS X and other UNIX variants.
\end{innerlist}


%
% Courses
%
\section{Courses}
\textit{Workshops / Lectures}
\begin{innerlist}
    \item RegStat 2011 - Extensions to Epidemiological Designs in Register-Based Research.
    \item ENGAGE IT-Course and Statistical Workshop: Tools for data analysis and management in complex traits genetic studies.
    \item Age Period-Cohort Modelling.
    \item Essentials of descriptive cancer epidemiology.
\end{innerlist}

\halfblankline

\textit{Courses}
\begin{innerlist}
    \item PDC Summer School - Introduction to High-Performance Computing.
    \item Epidemiological theory in a statistical framework.
\end{innerlist}


%
% Language skills
%
\section{Language Skills}
Swedish, English, Japanese (elementary)
